---
output: rmarkdown::github_document
editor_options: 
  chunk_output_type: console
---
```{r pkg-knitr-opts, include=FALSE}
hrbrpkghelpr::global_opts()
```

```{r badges, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::stinking_badges(branch = "batman")
```

```{r description, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::yank_title_and_description()
```

## What's Inside The Tin

The following functions are implemented:

```{r ingredients, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::describe_ingredients()
```

## Installation

```{r install-ex, results='asis', echo=FALSE, cache=FALSE}
hrbrpkghelpr::install_block()
```

## Usage

```{r lib-ex}
library(construe)

# current version
packageVersion("construe")

```

### Requests

```{r ex01}
paste0(c(
  "GET /uri.cgi HTTP/1.1\r\n",
  "User-Agent: Mozilla/5.0\r\n",
  "Accept: text/html,application/xhtml+xml,application/xml;q=0.9,*/*;q=0.8\r\n",
  "Host: 127.0.0.1\r\n", "\r\n"
), collapse = "") -> req

req_raw <- charToRaw(req)

parse_request(req)

parse_request_raw(req_raw)

microbenchmark::microbenchmark(
  parse_request = parse_request(req),
  parse_request_raw = parse_request_raw(req_raw)
)
```


### Responses

```{r ex02}
paste0(c(
  "HTTP/1.1 200 OK\r\n",
  "Server: nginx/1.2.1\r\n",
  "Content-Type: text/html\r\n",
  "Content-Length: 8\r\n",
  "Connection: keep-alive\r\n",
  "\r\n",
  "<html />"
), collapse = "") -> resp

resp_raw <- charToRaw(resp)

parse_response(resp)

parse_response_raw(resp_raw)

microbenchmark::microbenchmark(
  parse_response = parse_response(resp),
  parse_response_raw = parse_response_raw(resp_raw)
)
```

### curl output example

`HEAD` request:

```{r curl-01}
sys::exec_internal(
  cmd = "curl", 
  args = c("--include", "--head", "--silent", "https://httpbin.org/")
) -> res

rawToChar(res$stdout)
```

`GET` request:

```{r curl-02}
sys::exec_internal(
  cmd = "curl", 
  args = c("--include", "--silent", "https://httpbin.org/")
) -> res

parse_response_raw(res$stdout)
```

### URLs

```{r ex03}
c(
  "git+ssh://example.com/path/file",
  "https://example.com/path/file",
  "http://www.example.com/dir/subdir?param=1&param=2;param%20=%20#fragment",
  "http://www.example.com",
  "http://username@www.example.com/dir/subdir?param=1&param=2;param%20=%20#fragment",
  "http://username:passwd@www.example.com/dir/subdir?param=1&param=2;param%20=%20#fragment",
  "http://www.example.com:8080/dir/subdir?param=1&param=2;param%20=%20#fragment",
  "http://username:passwd@www.example.com:8080/dir/subdir?param=1&param=2;param%20=%20#fragment",
  "ftp://username:passwd@ftp.example.com/dir/filename.ext",
  "mailto:username@example.com",
  "svn+ssh://hostname-01.org/path/to/file",
  "xddp::://///blah.wat/?"
) -> turls

parse_url(turls)

microbenchmark::microbenchmark(
  parse_url = parse_url(turls[1])
)
```

### Parse headers from Palo Alto `HEAD` requests

```{r why}
hdr <- read_file_raw(system.file("extdat", "example.hdr", package = "construe"))

cat(rawToChar(hdr))

parse_response_raw(hdr)
```

## construe Metrics

```{r cloc, echo=FALSE}
cloc::cloc_pkg_md()
```

## Code of Conduct

Please note that this project is released with a Contributor Code of Conduct. 
By participating in this project you agree to abide by its terms.
